Hybrid platforms and bargaining power

### 2024-01-12 src/paper/application.tex
Add low lambda extension

TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Platform profits}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.5, % adjust these values as needed
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=south east,
                    width=\linewidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Optimal/implied entry fee}
    \end{subfigure}
    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$). Regardless of lambda, platform profits and entry fees are increasing in $N_P$. However, when the platform's innate bargaining power is higher, entry fees are above optimal levels already for $N_P = 0$, and the additional increase somewhat mitigates the benefits of the platform's increased product variety. When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits. Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
    \label{fig:platform_profits_low_lambda}
\end{figure}

>>>>

\textcolor{red}{TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.}

The example parametrizatrion is the same as in the main model, with the only difference that the platform has a lower innate bargaining power ($\lambda_P = 0.5$).
As the conditions in \cref{ass:single_crossing} are also satisfied in this case, the main observations from \cref{sec:results} also apply.
That is, as shown on \cref{fig:fringe_entry_eq_low_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.

The main difference is that, due to the lower bargaining power of the platform, the implied entry fee (\cref{fig:platform_profits_low_lambda}) is lower than the benchmark, unilaterally set one for low enough $N_P$.
As a consequence, total aggregate, and thus consumer surplus, is also above the benchmark outcome in that case.
Furthermore, there exists some $\bar{N}_P$ for which the unilateral price setting and bargaining outcomes coincide in terms of all variables, due to the implied entry fee being the same.

Another major difference pertains to the total profits of the platform as a function of $N_P$.
It is still true that they are increasing in the number of the platform's products, but now this increase is even more pronounced for low values of $N_P$.
The reason is that for low $N_P$, the implied entry fee is lower than the optimal one.
Furthermore, it increases in $N_P$ as a result of the platform's increased bargaining power.
Therefore, the platform's profits are increasing in $N_P$ even more than in the benchmark case or the main model, up to the point where the implied entry fee is equal to the optimal one.
After that, the same effect as in the main model kicks in, and the increase in profits is lower than in the benchmark case.

\Cref{fig:equilibrium_low_lambda_entry_fees} demonstrates an important consequence of this phenomenon.
Imagine that the platform can decide on the number of its products at time 0, at an investment cost of $I_P$ per product.
In the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation is never optimal.
The platform would always prefer either pure retail or pure marketplace operation.
In contrast, when the platform has lower bargaining power, there exists a range of $I_P$ values (e.g. $I_P = 0.2$) for which the platform would prefer to operate in hybrid mode.
Furthermore, if hybrid operation is not allowed, the platform might switch to become a pure marketplace, thereby increasing consumer surplus.

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Platform profits}
        \label{fig:platform_profits_low_lambda}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.5, % adjust these values as needed
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=south east,
                    width=\linewidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Optimal/implied entry fee}
        \label{fig:entry_fee_low_lambda}
    \end{subfigure}
    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$). Regardless of lambda, platform profits and entry fees are increasing in $N_P$. However, when the platform's innate bargaining power is higher, entry fees are above optimal levels already for $N_P = 0$, and the additional increase somewhat mitigates the benefits of the platform's increased product variety. When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits. Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
    \label{fig:profits_and_entry_fees_low_lambda}
\end{figure}
